Meta-analysis of the Interoceptive Accuracy Scale

### 2025-01-15 analysis/Study1.qmd
updated manuscript + added extension

desc_df1a <- desc(df1a)
desc_df1b <- desc(df1b)
desc_df2 <- desc(df2)
desc_df3 <- desc(df3)
#desc_df4 <- desc(df4)
desc_df5 <- desc(df5_attention)
desc_df6 <- desc(df6)
desc_df7a <- desc(df7a)
desc_df7b <- desc(df7b)
desc_df7c <- desc(df7c)
desc_df8a <- desc(df8a)
desc_df8b <- desc(df8b)
desc_df9 <- desc(df9)
desc_df10a <- desc(df10a)
desc_df10b <- desc(df10b)
desc_df10c <- desc(df10c)
desc_df11a <- desc(df11a)
desc_df11b <- desc(df11b)

>>>>

desc_df1a <- desc(df1a)
desc_df1b <- desc(df1b)
desc_df2 <- desc(df2)
desc_df3 <- desc(df3)
#desc_df4 <- desc(df4) # no demographic data available
desc_df5 <- desc(df5_attention)
desc_df6 <- desc(df6)
desc_df7a <- desc(df7a)
desc_df7b <- desc(df7b)
desc_df7c <- desc(df7c)
desc_df8a <- desc(df8a)
desc_df8b <- desc(df8b)
desc_df9 <- desc(df9)
desc_df10a <- desc(df10a)
desc_df10b <- desc(df10b)
desc_df10c <- desc(df10c)
desc_df11a <- desc(df11a)
desc_df11b <- desc(df11b)

### 2025-01-15 analysis/study2.qmd
updated manuscript + added extension

>>>>

## Measures used

```{r}
library(gt)

# APA style ####
gt_apastyle <- function(gt_table, font.size=12) {
  gt_table  |> 
    gt::opt_table_lines(extent = "none") %>%
    gt::tab_options(
      heading.border.bottom.width = 2,
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table.border.top.style = "solid",
      table.border.top.width = 2,  
      table_body.hlines.color = "white",
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.top.width = 2,
      heading.title.font.size = font.size,
      table.font.size = font.size,
      heading.subtitle.font.size = font.size,
      table_body.border.bottom.color = "black",
      table_body.border.bottom.width = 2,
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.bottom.width = 1,
      latex.use_longtable = FALSE
    ) |> 
      gt::opt_table_font(font = "times")
}

table <- data.frame(
  Questionnaire = c("Interoceptive Related", "MAIA-2", "BPQ", "TAS-20", "BVAQ",
                    "Mood", "BDI-II", "PHQ-4", "STAI-T", "GAD-2",
                    "Personality", "NEO-FFI", "Mini IPIP6", "BFI", "PID-5-SF",
                    "Psychopathology", "SPQ-BRU", "MSI-BPD", "ASQ - Short",
                    "Beliefs and Misbeliefs", "GCB", "PI-18", "LIE scale"),
  Number_of_Dimensions = c('', 8, 2, 3, 2, 
                           '', 1, 2, 1, 1, 
                           '', 1, 6, 5, 5, 
                           '', 4, 1, 5, 
                           '', 5, 1, 4),
  Assessment = c('', "Interoception", "Body awareness and autonomic reactivity", "Alexithymia", "Alexithymia",
                 '',"Severity of depressive symptoms", "Anxiety and depressive symptoms", "Trait anxiety", "General Anxiety",
                 '', "Neuroticism", "Personality", "Personality", "Dysfunctional personality traits",
                 '', "Schizotypy", "Borderline personality disorder", "Autistic Traits",
                 '', "Conspiracy beliefs", "Beliefs about the world", "Lying tendencies"),
  Number_of_Items = c('',37, 49, 20, 40, 
                      '',21, 4, 20, 2, 
                      '',12, 24, 44, 25, 
                      '',32, 10, 28, 
                      '',15, 99, 16),
  Scoring = c('',"6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", 
              '',"0-to-3-point values", "5-point Likert scale", "4-point Likert scale", "4-point Likert scale", 
              '',"5-point Likert scale", "Analogue scales", "5-point Likert scale", "4-point Likert scale", 
              '',"5-point Likert scale", "Analogue scales", "4-point Likert scale", 
              '',"5-point Likert scale", "6-point Likert scale", "Visual analogue scales"), 
  stringsAsFactors = FALSE
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Scoring") |> 
  cols_label(Number_of_Dimensions = "Number of Dimensions", Number_of_Items = "Number of Items")  |>
  # tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") 
  tab_style( style = list(cell_text(weight = "bold")), locations = cells_body(columns = Questionnaire, rows = Questionnaire %in% c("Interoceptive Related", "Mood", "Personality", "Psychopathology", "Beliefs and Misbeliefs")))

gt_apastyle(table_apa, font.size=12)
gtsave(gt_apastyle(table_apa, font.size=9), "figures/table2.tex")
```
